\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Jakub Kvita}

\section{Education}

\begin{yearlist}
	
	\item[Computer Science]{2014 -- 2016}
	{Master of Science}
	{\emph{Brno University of Technology}. Brno, Czech Republic.}
	
	\item[Computer Science]{2013 -- 2014}
	{Master of Science}
	{\emph{University of South Wales}. Cardiff, United Kingdom.}
	
	\item[Computer Science]{2010 -- 2013}
	{Bachelor of Science}
	{\emph{Brno University of Technology}. Brno, Czech Republic.}
	
\end{yearlist}

\section{Work experience}

\begin{eventlist}

\item{October 2017 -- present}
{Vestorly, Inc.}
{Infrastructure Engineer}

\emph{Czech Republic}. Working remotely from Czech Republic within the same team as before. Managing CircleCI pipeline upgrades and continuing with Docker/Kubernetes migration.

\item{October 2016 -- September 2017}
{Vestorly, Inc.}
{Infrastructure Engineer}

\emph{New York, USA}. I worked on infrastructure and automation of SaaS platform - AWS configuration, DNS management, CI/CD pipeline, email delivery and migration from Heroku to Kubernetes.

\item{July 2015 -- August 2015}
     {CERN -- European Org. for Nuclear Research}
     {OpenLab Summer Student}

\emph{Geneva, Switzerland}. I worked in the Cloud \& Virtualization team on configuring backends and backups for Openstack Cinder volumes.
%(Tape storage and massive HDD arrays.)


\item{June 2014 -- June 2015}
     {Red Hat, Inc.}
     {Quality Assurance Engineer}

\emph{Brno, Czech Republic}. Writing test cases for Pulp project and validating CDN and customer subscriptions. Automation with Python test frameworks.

%\item{February 2015 -- June 2015}
%     {Red Hat, Inc.}
%     {Quality Assurance Engineer}
%
%\emph{Brno, Czech Rep.} Writing test cases for Pulp project. I worked on REST API Python tests, using Jenkins and Gerrit.
%
%\item{June 2014 -- January 2015}
%     {Red Hat, Inc.}
%     {Quality Assurance Engineer}
%
%\emph{Brno, Czech Rep.} Testing subscriptions of customers and CDN content using Python. Planning in Redmine/Trac and Bugzilla. Distributed team.

\end{eventlist}

\section{Languages}

\begin{factlist}
	\item{Czech}{First language.}
	\item{English}{Fluent. Cambridge English C1.}
	\item{Slovak}{Proficient.}
	\item{Russian}{Basic communication skills.}
\end{factlist}

\personal
[kvitajakub.github.io]
{468W 47th St\newline New York, NY, 10036 USA}
{+420 702 973 246}
{kvitajakub@gmail.com}
{linkedin.com/in/kvitajakub}

\section{Courses and Certificates}

\begin{yearlist}
	
	\item{2014}
	{Computer Vision and Intelligent Computer Systems}
	{Intensive course at \emph{University of Burgundy}. Le Creusot, France}
	
	\item{2013}
	{Cambridge ESOL FCE.}
	{Certificate in English, level C1.}
	
	\item{2013}
	{Cisco Certified Network Associate}
	{CCNA Routing and Switching.}
	
\end{yearlist}

\section{Software skills}

\begin{factlist}
	
	\item{Languages}
	{Ruby, Bash, SQL, C.}
	
	\item{Software}
	{Git, Linux, Nginx, CircleCI\newline AWS, Docker, Kubernetes, Prometheus, Ansible, MongoDB.}
	
	\item{Concepts}
	{Containers, CI/CD, DNS,\newline web applications, networking, reliability, scalability.}
	
\end{factlist}

\section{School/Side Projects}

\begin{eventlist}

	\item{2017}
	{}
	{Release notes generator}
	
	Release notes generation based on merged pull requests using Github API. CI/CD webhooks and time based triggers.

	\item{2016}
	{Masters Thesis}
	{{\href{https://github.com/kvitajakub/MasterThesis}{Image Captioning with Recurrent\newline Neural Networks}}}
	
	LSTM models generating text on character level created in Torch. Experiments with initialization of the model by CNN output and bag-of-words vector for image captioning purposes. 
	
	\item{2013}
	{Bachelors Thesis}
	{{\href{https://github.com/kvitajakub/LSystemModeller}{Generator of 3D objects based on L-Systems}}}
	
	Interactive application for generating and viewing 3D models using OpenGL. Fractal modeling and plant growth simulation through L-system rules.
	
\end{eventlist}

\end{document}
